Distributed Version Control Systems

### 2010-05-16 paper.tex
Extendida la seccion Centralized repository with integration manager
agregada seccion de comparativa

>>>>

\section{Comparison}

\subsection{Commits}
In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.

Also, DVCS allow to apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
